Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
added Multilayer neural field model
added Multilayer caption
added field estimation over all time

Typically, the experimentalist only has access the net field generated by the multi-resolution architecture. Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system. The solution to this problem was proposed by \dean{Breakspear and Stam} in using a wavelet decomposition.  
\begin{figure}[t]
	\centering
		\includegraphics[scale=0.65]{./Graph/MultiresNeuralField.pdf}
	\caption{Multi-layer neural field model.}
	\label{fig:MultiLayerFieldModel}
\end{figure}

@@

By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
\begin{align}\label{eq:MRA-QDerivative}
\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
\end{align}
Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
\begin{align}\label{eq:MRA-thetahat}
\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
\end{align}
The second derivative of the $\mathcal Q$-function is given by
\begin{equation}
\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
\end{equation}
The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 2), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator. Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.

@@

>>>>

Typically, the experimentalist only has access the net field generated by the multi-resolution architecture. Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system. The solution to this problem was proposed by \dean{Breakspear and Stam} in using a wavelet decomposition.  
\begin{figure}[t]
	\centering
		\includegraphics[scale=1]{./Graph/MultiResNeuralField.pdf}
	\caption{{\bf Multi-layer neural field model}. The inset figures show the shape of the
connectivity kernel components at each spatial resolution.}
	\label{fig:MultiLayerFieldModel}
\end{figure}

@@

By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
\begin{align}\label{eq:MRA-QDerivative}
\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
\end{align}
Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
\begin{align}\label{eq:MRA-thetahat}
\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
\end{align}
The second derivative of the $\mathcal Q$-function is given by
\begin{equation}
\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
\end{equation}
The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 2), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator. Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.

@@

\begin{figure}[t]
		\includegraphics[scale=1]{./Graph/STMultiRes.png}
	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}. (\textbf{A}) The reconstructed field of the reduced model using only scaling functions at $j=0$. (\textbf{B}) The reconstructed field using scaling and wavelet functions at $j=0$. (\textbf{C}) The reconstructed field using scaling and wavelet functions at $j=1$. (\textbf{D}) The reconstructed field using scaling and wavelet functions at $j=2$. (\textbf{E}) The reconstructed field using scaling and wavelet functions at $j=3$. (\textbf{F}) The actual field.}
	\label{fig:FieldEstimation}
